
\documentclass[a4paper,22pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Rakshit Yadav}} & Email: \href{mailto:}{rakshityadav411@gmail.com } 
  \\
  \href{https://www.linkedin.com/in/rakshityadavv/}{Linkedin} \hspace{1pt} \href{https://github.com/RakshitYadav09}{Github} \hspace{1pt} \href{https://www.behance.net/rezzfx}{Behance} &  Mobile: +91-9312354133 \\ \\
\end{tabular*}

\section{Skills}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages}{~~~~~~Python, C++, JavaScript, MySQL, R}
	\resumeSubItem{Frameworks}{~~~~PyTorch, Scikit-learn, Angular, React, Django, Node.js}
	\resumeSubItem{Tools}{~~~~~~~~~~~~~~Figma, Power BI, AWS S3 }
	\resumeSubItem{Soft Skills}{~~~~~~~Time Management, Communication, Adaptability, Interpersonal Skills.}
\resumeSubHeadingListEnd
\vspace{5pt}


\vspace{-5pt}
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading{SNUG Technologies Private Limited}{Gurugram, Haryana (On-Site)}
    {Full Stack Developer-Intern}{June 2024 - July 2024}
    \resumeItemListStart
             \resumeItem{Responsibilities}
          {\newline
          - Played a key role in enhancing SnugDesk by upgrading its architecture from Angular 15 to Angular 17, focusing on delivering a more responsive and efficient user experience. \newline
    - Spearheaded the integration of Server-Side Rendering (SSR) with Angular Universal, which led to a 30\%  increase in page load speeds and improved search engine rankings. \newline
    - Collaborated with the development team to adopt the latest Angular framework practices, resulting in a more maintainable and scalable codebase.\newline
    - Conducted rigorous testing and performance analysis to ensure the upgraded application met all functional and non-functional requirements.}
      \resumeItemListEnd
      \vspace{5pt}
       \resumeSubheading{Colt India}{Gurugram, Haryana (On-Site)}
    {Operations and Testing - Intern}{December 2023 - February 2024}
    \resumeItemListStart
             \resumeItem{Responsibilities}
          {\newline
          - Completed a comprehensive internship specializing in software testing, test automation, and operational workflows.. \newline
    - Executed manual and regression testing techniques to rigorously validate software deliverables, ensuring high-quality, bug-free releases. \newline
    - Took part in the optimization of CI/CD pipelines, reducing deployment times and enhancing operational efficiency by collaborating with a cross-functional team. \newline
    - Developed and implemented automation scripts using Python, increasing test coverage and reducing manual testing efforts by 30\%. \newline
    - Documented and communicated detailed test plans, test cases, and defect reports, contributing to improved project documentation and team awareness.}
      \resumeItemListEnd
 \vspace{5pt}
\resumeSubHeadingListEnd
\vspace{-5pt}
%-----------PROJECTS-----------------
\vspace{-5pt}
\section{Projects}
\resumeSubHeadingListStart
\resumeSubItem{\href{https://github.com/RakshitYadav09/price-predictor}{Property Price Predictor}(Python, Pandas, Scikit-learn)}{ \newline
    - Developed a robust real estate price prediction tool, leveraging regression models to predict housing prices based on data. \newline
        - Utilized Pandas for efficient data manipulation, cleaning, and pre-processing, ensuring quality input data for model training.\newline
    - Implemented multiple regression models using Scikit-learn, comparing their performance to optimize prediction accuracy.\newline
    - Demonstrated expertise in data wrangling, feature engineering, and model evaluation, resulting in a reliable tool for real estate market analysis. }
\vspace{2pt}
\resumeSubItem{\href{https://www.behance.net/gallery/201845335/Explore-India-A-traveling-website-inspired-by-India/modules/1144905721}{Explore India}(Figma, UI/UX Development)}{\newline 
     - Designed and developed an intuitive, user-centric tourism website focused on enhancing the travel experience across India. \newline
        - Conducted thorough user research and created wireframes and prototypes to ensure the website’s design was aligned with user needs and preferences.\newline
    - Implement modern design techniques to develop a user friendly and appealing design which attracts more users.\newline
    - Integrated interactive features such as maps, travel itineraries, and cultural insights, enhancing user engagement and usability. }
\vspace{2pt}
\resumeSubItem{\href{https://www-dev.snugdesk.com/}{SnugDesk}(Angular 17, Express Js, Amazon S3)}{\newline 
    - Took part in the upgrade of SnugDesk from Angular 15 to Angular 17, incorporating Server-Side Rendering (SSR) to boost performance and SEO.\newline
    - Integrated Amazon S3 to optimize data management, ensuring efficient storage and retrieval of large datasets.
\newline
    - Implemented Server-Side Rendering (SSR) using Angular Universal, contributing to a notable improvement in both user experience and SEO performance.\newline
   - Executed comprehensive testing protocols and conducted in-depth performance assessments, ensuring that all new features and enhancements were fully aligned with project goals and client expectations.   }
\vspace{2pt}
\resumeSubHeadingListEnd
%-----------Awards---
%-----------EDUCATION-----------------
\section{~~Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {SRM Institute of Science and Technology}{Kattankulathur, Chennai}
      {BTech Computer Science with specialization in Software Engineering}{September 2022 - June 2026}
    \resumeSubHeadingListEnd
\end{document}
